---
title: "Research Preparation"
author: "Michiru Nozawa"
format: html
editor: visual
---

### Main Question

**How COVID-19 affects the centrality in ASEAN+3?**

We are goign to use 2018 data as the evidence of the ASEAN+3 network before COVID-19 and 2019-2021 data as the evidence of of their network after COVID-19.

Use modularity to measure the tie and detect the community! Also, look at the polarization in ASEAN+3 network.

### Load Packages

```{r, message = FALSE}
library(rio)
library(igraph)
library(tidyverse)
library(dplyr)
library(statnet)
```

### Import data

```{r, message = FALSE, warning=FALSE, echo=FALSE}
# 2018 data as BEFORE COVID
df2018 <- import("BACI_HS17_Y2018_V202301.csv")

# 2019-2021 data as AFTER COVID
df2019 <- import("BACI_HS17_Y2019_V202301.csv")
df2020 <- import("BACI_HS17_Y2020_V202301.csv")
df2021 <- import("BACI_HS17_Y2021_V202301.csv")
```

We would like to focus on the trading of ASEAN+3, first we are going to filter the countries to clean our data.

Right now, 13 countries are the part of ASEAN+3.

-   Indonesia 360

-   Malaysia 458

-   Philippine 608

-   Singapore 702

-   Thailand 764

-   Brunei 96

-   Vietnam 704

-   Laos 418

-   Myanmar 104

-   Cambodia 116

-   China 156

-   Korea 410

-   Japan 392

### Variables in data

-   t: Year
-   i: Exporter
    -   Limited to ASEAN+3 members which are listed above
-   j: Importer
    -   Also limited to ASEAN+3 members
-   k: Product category
    -   We might want to remove this variable if we do not care about product category in our research
-   v: Value of the trade flow
    -   How did they measure the value of the trade flow?

    -   If we remove product category, we can find the aggregate of the value of the trade flow

    -   Every value is recorded
-   q: Quantity in metric tons (1 MT = 1000 kg)
    -   Remove product category and find the aggregate quantity?

    -   Adding the quantity of every product might cause the issue since one heavy product can have same quantity as 100 light products.

    -   Some missing values -- how should we handle them? Keep them as NA or change to 0?

```{r}
# question: how do we convert this data into network data? 
APT_2018 <- df2018[, -c(4, 6)] %>%
  filter(i %in% c(360, 458, 608, 702, 764, 96, 704, 418, 104, 116, 156, 410, 392)) %>%
  filter(j %in% c(360, 458, 608, 702, 764, 96, 704, 418, 104, 116, 156, 410, 392))


APT_2018_new <- APT_2018 %>% 
  group_by(i, j) %>%
  summarise(total_value_trade_flow = sum(v))
  
```

```{r cleaning data}
df2018 = subset(df2018, select = c(t:j, v:q))

df2018_trade_df <- df2018 %>%
  group_by(i, j) %>%
  summarise(total_trade_value = sum(v)) %>%
  filter(i %in% c(360, 458, 608, 702, 764, 96, 704, 418, 104, 116, 156, 410, 392)) %>%
  filter(j %in% c(360, 458, 608, 702, 764, 96, 704, 418, 104, 116, 156, 410, 392))
```

```{r data conversion}
# convert data frame into network object
APT_2018_net <- as.network(df2018_trade_df, mode = c("directed"))
```

```{r visualization}
set.seed(1556)
plot(APT_2018_net, label = network.vertex.names(APT_2018_net))
title(main="ASEAN+3 Network in 2018")
```

TO-DO: - Git hub - Add country name to the data frame - Find the weighted ties - Create visualization for every year and find the visualization format (4) - Create the aggregated visualization (1) - Use modularity and centrality to identify the network's central actor as well as the communities
